---
title: "TP_25_15_2020"
author: "FHS"
date: "25 novembre 2020"
output:
  prettydoc::html_pretty
---
# Kmeans Clustering

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**1.** Download the dataset 

```{r, echo=T,eval=T} 
ligue1 <- read.csv("http://mghassany.com/MLcourse/datasets/ligue1_17_18.csv", row.names=1, sep=";")

#summary(ligue1)
```

**2.** Print the first two rows of the dataset and the total number of features in this dataset.

```{r}

knitr::kable(ligue1[1:2,]) #Two first rows

dim(ligue1)
str(ligue1)


```

**3.** Create a new dataset in which you consider only Points and Yellow.cards from the original dataset. Name it pointsCards

```{r}
pointsCards=ligue1[,c(1,10)]

summary(pointsCards)
str(pointsCards)
```


**4.** Apply k-means on pointsCards.

```{r}
set.seed(123)
data <- data.frame(pointsCards)
km <- kmeans(data, centers = 2, iter.max=20)
```

**5.** Print and describe what is inside km.


```{r}
km
```

**6.** What are the coordinates of the centers of the clusters 

```{r}
km$centers
```

**7.** Plot the data (Yellow.cards vs Points). Color the points corresponding to their cluster.

```{r}
library(ggplot2)
plot(data,col=km$cluster,pch=20,cex=1)
points(km$centers,col=1:2,pch=3,cex=3,lwd=3)

```

**8.** Add to the previous plot the clusters centroids and add the names of the observations.


```{r}
ggplot(data, aes(x=Points, y = yellow.cards)) + geom_point(color=km$cluster) + geom_text(label = rownames(data), color=km$cluster) + geom_point(data=data.frame(km$centers), aes(x=Points, y = yellow.cards), fill =c('black','red'), color=c('black','red'), shape=23, size=5)
```



**9.** Re-run k-means on pointsCards using 3 and 4 clusters and store the results into km3 and km4 respectively. Visualize the results like in question 7 and 8.


```{r}

km3 <- kmeans(data, centers = 3, iter.max=20)
km4 <- kmeans(data, centers = 4, iter.max=20)

```


Visualization for km3 


```{r}
ggplot(data, aes(x=Points, y = yellow.cards)) + geom_point(color=km3$cluster) + geom_text(label = rownames(data), color=km3$cluster) + geom_point(data=data.frame(km3$centers), aes(x=Points, y = yellow.cards), fill =c('black','red','green'), color=c('black','red','green'), shape=23, size=5)
```

Visualization for km4 

```{r}

ggplot(data, aes(x=Points, y = yellow.cards)) + geom_point(color=km4$cluster) + geom_text(label = rownames(data), color=km4$cluster) + geom_point(data=data.frame(km4$centers), aes(x=Points, y = yellow.cards), fill =c('black','red','green','blue'), color=c('black','red','green','blue'), shape=23, size=5)

```

**10.** Visualize the “within groups sum of squares” of the  k-means clustering results (use the code in the link above).

```{r}
mydata <- pointsCards
wss <- (nrow(data)-1)*sum(apply(data,2,var))
   
for (i in 2:15){
    wss[i] <- sum(kmeans(data,centers=i)$withinss)
    }

plot(1:15, wss, type="b", xlab="Number of Clusters",
      ylab="Within groups sum of squares")
```

**11.** Modify the code of the previous question in order to visualize the ‘between_SS / total_SS’. Interpret the results.

```{r}
for (i in 1:15){
    wss[i] <- kmeans(mydata,centers=i)$betweenss/kmeans(mydata,centers=i)$totss
    } 
plot(1:15, wss, type="b", xlab="Number of Clusters",ylab="between_SS / total_SS")
```


#Ligue 1 

**12.** Scale the dataset and transform it to a data frame again. Store the scaled dataset into ligue1_scaled

```{r}

ligue1_scaled <- data.frame(scale(ligue1))
```

**13.** Apply kmeans() on ligue1 and on ligue1_scaled using 3 clusters and 20 iterations. Store the results into km.ligue1 and km.ligue1.scaled respectively (do not forget to set a seed)

```{r}
km.ligue1 <- kmeans(ligue1, centers = 3, nstart = 20)
km.ligue1.scaled <- kmeans(ligue1_scaled, centers = 3, nstart = 20)
table(km.ligue1$cluster)
```

# PCA

**14. **


**15. **

```{r}
pcaligue1<- princomp(ligue1,cor = T)
```

**16. **

```{r}
require(factoextra)
fviz_pca_biplot(pcaligue1, repel = TRUE,
                col.var = "#2E9FDF", 
                col.ind = "#696969")

```




**17.** 

```{r echo=T,eval=T}
library(factoextra)
fviz_cluster(km.ligue1, data = ligue1, # km.ligue1 is where you stored your kmeans results
              palette = c("red", "blue", "green"), # 3 colors since 3 clusters
              ggtheme = theme_minimal(),
              main = "Clustering Plot"
)


```

**18**. 



```{r}

kme2 <- kmeans(pcaligue1$scores[, 1:2], centers = 3, nstart = 20)
fviz_cluster(kme2, data = pcaligue1$scores[, 1:2], 
              palette = c("red", "blue", "green"), 
              ggtheme = theme_minimal(),
              main = "Clustering Plot On First 2 PCs"
)

```



#Hierarchical clustering on Iris dataset

```{r}
iris <- read.csv("iris.data")
```

**2. **
```{r}
set.seed(223)
sampleiris<- iris[sample(1:150,40),]
```

**3. **
```{r}
D<- dist(sampleiris[,-5])
```

**4. **
```{r}
dendro.avg<- hclust(D,method="average")
```

**5. **
```{r}
plot(dendro.avg)
```

**6. **
```{r}
plot(dendro.avg, hang=-1, label=sampleiris$class)

```

**7. **
```{r}
groups.avg <- cutree(dendro.avg, k = 3)

```

**8. **
```{r}
plot(dendro.avg, hang=-1, label=sampleiris$class)
rect.hclust(dendro.avg, 3)
rect.hclust(dendro.avg, 3, border = c ("blue", "green", "red"))

```


**9. ** 
```{r}
table(groups.avg, sampleiris$class)

```




