---
title: "PW8"
author: "Soulaimane"
date: "2 décembre 2020"
output:
  prettydoc::html_pretty
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


**1.** Download and import Data1  and Data2 . Plot both of the datasets on the same window. Color the observations with respect to the ground truth, like in Figure 8.6.


```{r}

data1=read.csv("data1.csv")
data2=read.csv("data2.csv")
par(mfrow=c(1,2))
plot(data1[,1:2],pch=21,bg=data1$truth,main="Data1")
plot(data2[,1:2],pch=21,bg=data2$truth,main="Data2")



```




**2.** Applyk-means on both datasets with 4 clusters. Plot both of the dataset on the same window and color the observations with respect to k-means results. Interpret the results.



```{r}
set.seed(123)
km1<-kmeans(data1[,1:2],4)
km2<-kmeans(data2[,1:2],4)
par(mfrow=c(1,2))
plot(data1[,1:2],pch=21,bg=km1$cluster)
plot(data2[,1:2],pch=21,bg=km2$cluster)

```



**3.** Now fit a GMM model on the datasets.



```{r}

library(mclust)

gmm1 <- Mclust(data1[,1:2]) #optimal model according to BIC 

gmm2 <- Mclust(data2[,1:2]) #optimal model according to BIC 

par(mfrow=c(1,2))
plot(data1[,1:2], pch=21, bg=km1$classification)
plot(data2[,1:2], pch=21, bg=km2$classification)

```


**4.** Show the summary of the GMM model you fitted on Data2. Explain what it shows.

```{r}
summary(gmm2)

```

**5** To plot your two-dimensional data, use the standard plot function applied on your model.

```{r}
library(mclust)
gmm_model <- Mclust(data2[,1:2])

plot(gmm_model,what="classification")
plot(gmm_model,what="uncertainty")
```


**6.** To see the values of BIC for different number of mixtures use the following code.

```{r}
plot(gmm_model,what="BIC")
```

**7.** 

```{r}
dens2 <- densityMclust(data2[,1:2])
plot(dens2, what = 'density',data = data2[,1:2], type = "hdr", prob = seq(0.1, 0.9, by = 0.1), col = "slategrey")
plot(dens2, what = 'density',data = data2[,1:2], type = "persp", prob = seq(0.1, 0.9, by = 0.1))
```

***8 et 9 ***

```{r}
n<-100
set.seed(123)
y<-c(rnorm(n,-5),rnorm(n,0),rnorm(n,5))
yclass <- c(rep(1,n),rep(2,n),rep(3,n))
stripchart(y,pch=21,bg=yclass)

```

**10** Plot the histogram corresponding to your generated data. Interpret it.

```{r}
hist(y,30,probability = T)
```


**11.** Fit a GMM model on your generated data. Print the summary and visualize your results. Explain your results.


```{r}
ymodel <-Mclust(y)
par(mfrow=c(2,2))
plot(ymodel,what="BIC")
plot(ymodel,what="classification")
plot(ymodel,what="uncertainty")
plot(ymodel,what="density")

```

**12.**Apply a density estimate on your generated data and visualize it. Interpret the obtained figure.

```{r}
yModelDensity <-densityMclust(y)
plot(yModelDensity,what="density",data=y,breaks=20)

```


